\documentclass{amsart}
\usepackage{amsfonts, amsmath, latexsym, epsfig}
\usepackage{epsf}
\usepackage{url}
\usepackage{color}
\title{Lattice Packings and Coverings}
%\usepackage{vmargin}
%\setpapersize{custom}{21cm}{29.7cm}
%\setmarginsrb{1.7cm}{1cm}{1.7cm}{3.5cm}{0pt}{0pt}{0pt}{0pt}
%marge gauche, marge haut, marge droite, marge bas.

\author{Mathieu Dutour Sikiri\'c}
\author{Frank Vallentin}
\author{Achill Sch\"urmann}




\begin{document}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\Q}{\ensuremath{\mathbb{Q}}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}
\newcommand{\T}{\ensuremath{\mathbb{T}}}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{problem}{Problem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{claim}{Claim}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}
%\newcommand{\qed}{\hfill $\Box$ }
%\newcommand{\proof}{\noindent{\bf Proof.}\ \ }

\maketitle



A family of balls in Euclidean space is called a packing if for
any two balls $B$ and $B'$ their interior do not self-intersect. It is called
a covering if every point belong to at least one ball.

We focus here on packings and coverings for which the calls are of the form
$x + B(0,R)$ with $x$ belonging to a lattice $L$.
If $L$ is fixed then we adjust the
value of $R$ to a value $R_0$ to find the best packing. Alternatively we can
adjust the value of $R$ to a value $R_1$ to find the best covering. This allows
us to define the packing density $pack(L)$ and covering density $cov(L)$ of $L$.

The geometry of the function pack on the space of lattices has been
elucidated by Minkowski, Voronoi and Ash. They showed that the function
$pack$ has no local minimum, that it is a Morse function and they give
a characterization of the local maximum in terms of the algebraic notions
of perfection and eutaxy.

The covering function $cov$ is much more complex. It has local minimum and
local maximum. We prove that it is not a Morse function.
The natural optimization problem for covering is to find local minima of
$cov$ but we show that the local covering maxima of $cov$ are also interesting.
In particular we prove the following theorem:
\begin{theorem}
A lattice $L$ is a covering maxima if and only if all of its Delaunay polytopes of maximal circumradius are perfect and eutactic.
\end{theorem}
Examples of perfect and eutactic Delaunay polytopes
are $2_{21}$ in $3_{21}$ in the
root lattices $E_6$ and $E_7$, which are thus local covering maxima.




\end{document}






